MADA Data Analysis Project

### 2021-11-02 code/processing_code/ProcessingScript.Rmd
clarify

```
####
__Eventually this will read in the combined dataframe made from separate reports__

@@

head(rawdata)
tail(rawdata)
summary(rawdata)
```
## Wrangle Data
```{r wrangle data}
All.PCR<-rawdata%>%
  #select data cols that will be relevant for analysis
  select(Phase:Ct)%>%
  #change some of the data types into other data types
  mutate(Phase=as.factor(Phase), 
         Plate=as.factor(Plate),
         Method=as.factor(Method),
         Tool=as.factor(Tool),
         Input=as.numeric(Input),
         Dilution=as.numeric(Dilution),
         Detector=as.factor(Detector),
         Ct=as.numeric(Ct))%>%
  glimpse()
#leaving Ct as Character, for not
summary(All.PCR)
```
## Split Data and Save

>>>>

```
####
__Eventually this will read in the combined data frame made from separate reports__

@@

head(rawdata)
tail(rawdata)
summary(rawdata)
```
## Wrangle Data
```{r wrangle data}
All.PCR<-rawdata%>%
  #select data cols that will be relevant for analysis
  select(Phase:Ct)%>%
  #change some of the data types into other data types
  mutate(Phase=as.factor(Phase), 
         Plate=as.factor(Plate),
         Method=as.factor(Method),
         Tool=as.factor(Tool),
         Input=as.numeric(Input),
         Dilution=as.numeric(Dilution),
         Detector=as.factor(Detector),
         Ct=as.numeric(Ct))%>%
  glimpse()
#leaving Ct as Character, for not
summary(All.PCR)
```
```{r All Data}
save_data_location <- here::here("data","processed_data","ALL.Data-20211029.rds")

saveRDS(All.PCR, file = save_data_location)
```

## Split Data and Save

### 2021-11-02 products/Project_Parts/Part_3/Part3.Rmd
clarify

---
title: "Data Exploration"
subtitle: ""
author: Monica Chan
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::html_document2: 
    toc: false
  bookdown::word_document2: 
    toc: false
    number_sections: true
bibliography: ../references.bib
csl: ../apa.csl
---
# Data Exploration
Complete the data loading/cleaning/wrangling part, as well as having a mostly complete data exploration part.

>>>>

---
title: "Part 3"
subtitle: ""
author: Monica Chan
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::html_document2: 
    toc: false
  bookdown::word_document2: 
    toc: false
    number_sections: true
bibliography: ../references.bib
csl: ../apa.csl
---
# Data Exploration
Complete the data loading/cleaning/wrangling part, as well as having a mostly complete data exploration part.

### 2021-11-02 products/manuscript/Manuscript.Rmd
clarify

There are 3 major aims of this:

1. Do the sample enhancement strategies work?
2. How well do they work compared to each other?
3. Are there any environmental variables recorded that have a positive impact on detection?

@@

Using established standard methods for environmental sampling with a self-contained polyurethane swab, a TC approach (NTP; Nanotrap® Magnetic Virus Particles, Ceres Nanosciences) was compared to an automated extraction method (MX48; Maxwell® RSC Viral Total Nucleic Acid Purification Kit, Promega) for recovery of heat-inactivated SC2 from the polyurethane swab as detected by rRT-PCR

## Data aquisition
Reports per each rRT-PCR run were generated and quality checked on their respective machines before transfer to a Teams repository. Summary data was selected from the reports and added to additional environmental data gathered on based on the extraction date of the sample.
Completed run data is then collated into one file and red into R.

@@

processingscript.R was modified to do initial cleaning and preparation of the dataset for further exploration.Data is also saved.

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._

@@

>>>>

There are several major aims of this:

1. Do the sample enhancement strategies work?
2. How well do they work compared to each other?
3. Are there any environmental variables recorded that have a positive impact on detection?
4. Can this data be modeled to back calculate a sample's original concentration based on the Ct values recovered?

@@

### Experiment setup and conditions

Using established standard methods for environmental sampling with a self-contained polyurethane swab from stainless steel surface, a TC approach (NTP; Nanotrap® Magnetic Virus Particles, Ceres Nanosciences) was compared to an automated extraction method (MX48; Maxwell® RSC Viral Total Nucleic Acid Purification Kit, Promega) for recovery of heat-inactivated SC2 from the polyurethane swab as detected by rRT-PCR

## Data aquisition
Reports per each rRT-PCR run were generated and quality checked on their respective machines before transfer to a Teams repository. Summary data was selected from the reports and added to additional environmental data gathered on based on the extraction date of the sample.

Completed run data is then collated into one file and read into R./A composited data set was compiled and saved as a csv and used as the base data for the project

@@

processingscript.R was modified to do initial cleaning and preparation of the dataset for further exploration.

Data was imported and cleaned.
Data was then split between the two different experimental types (P1 and P2).

This can be found in processing_code/ProcessingScript.RMD

### Data exploration

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others.

@@

#### All Data

Overview - split between part 1 and part 2

```{r ALLsummarytable,  echo=FALSE}
resulttable=readRDS("../../results/ALLsummarytable.rds")
knitr::kable(ALLresulttable, caption = 'ALL Data summary table.')
```

##### Serial Dilutions confirmation

Summary table 
scatter plot of SDs based ond dilution factors

#### Phase 1

### Phase 2

### Data Analysis

### Data Modeling
